DeepRain

### 2019-08-27 Docs/Langdokumentation.tex

\hypersetup{
    pdfauthor    = {Thomas Gnaedig, Etienne Gramlich, Tim Hardenacke, Merle Wolf},
    pdftitle     = {DeepRain},
    pdfsubject   = {Deep Learning},
    pdfkeywords  = {Deep Learning,rain},
    pdflang      = {de},         % Set language of document to German
    pdfstartview = {FitH},       % Fit the document to screen horizontally (page width)
    pdfview      = {FitH},       % Fit the document to screen horizontally (page width)
    colorlinks   = {true},       % Use color for links
    linkcolor    = {black},      % Links in black (text color)
    urlcolor     = {black},      % URLs in black (text color)
    citecolor    = {black},      % Citations in black (text color)
    filecolor    = {black},      % File links in black (text color)
}

@@

@@

% Datenanalyse

% Netzwerke
\input{Architekturen.tex}
\input{Klassifizierung.tex}

>>>>

\hypersetup{
    pdfauthor    = {Thomas Gnaedig, Etienne Gramlich, Tim Hardenacke, Merle Wolff},
    pdftitle     = {DeepRain},
    pdfsubject   = {Deep Learning},
    pdfkeywords  = {Deep Learning,rain},
    pdflang      = {de},         % Set language of document to German
    pdfstartview = {FitH},       % Fit the document to screen horizontally (page width)
    pdfview      = {FitH},       % Fit the document to screen horizontally (page width)
    colorlinks   = {true},       % Use color for links
    linkcolor    = {black},      % Links in black (text color)
    urlcolor     = {black},      % URLs in black (text color)
    citecolor    = {black},      % Citations in black (text color)
    filecolor    = {black},      % File links in black (text color)
}

@@

%Einleitung zu DeepLearning
\input{Abstract.tex}

@@

% Datenanalyse
\input{Datenanalyse.tex}
% Netzwerke
\input{Architekturen.tex}
\input{Klassifizierung.tex}
